```{r}
library(tidyr)
library(stringr)
library(skimr)
library(dplyr)
library(plotrix)
library(ggplot2)
library(radarchart)
library(gridExtra)
library(reshape2)
library(DataCombine)
library(grid)
library(ggraph)

```

#### Below codes are to calulate personal freedom and choice and personal safety####

##### FOR VULNERABLE EMPLOYBILITY #######

```{r}
vulnerability_employments_index <- select(vulnerability_employments, c(2, 55:62)) 
```

```{r}
colnames(vulnerability_employments_index)[1:9]<- c("code","2010","2011","2012","2013","2014","2015","2016","2017")
vulnerability_employments_index<- gather(vulnerability_employments_index,"year","vulnerability_employment",2:9)
```


```{r}
index_vulnerability<- function (actual_value){
  ind<- (actual_value - 94.7)/(0-94.7)
  return(ind)
}
```

```{r}
vulnerability_employments_index$vulnerability_employment<-index_vulnerability(vulnerability_employments_index$vulnerability_employment)
vulnerability_employments_index$year <- as.integer(vulnerability_employments_index$year)
```



####-----Freedom from forced labor---###

```{r}
freedom_forced_labor<- select(freedom_from_forced_labor, 2:4)
freedom_forced_labor<- filter(freedom_forced_labor, year %in% c(2010,2011,2012,2013,2014,2015,2016,2017))
```

```{r}
colnames(freedom_forced_labor)[1:3]<- c("code","year","freedom_forced_labor")
```

```{r}
index_labor<- function (actual_value){
  ind<- (actual_value - 0)/(1-0)
  return(ind)
}
```

```{r}
freedom_forced_labor$freedom_forced_labor<-index_labor(freedom_forced_labor$freedom_forced_labor)
freedom_forced_labor$year <- as.integer(freedom_forced_labor$year)
```



######---Freedom of discussion---####



```{r}
freedom_discussion<- select(freedom_of_discussion, 2:4)
freedom_discussion<- filter(freedom_discussion, year %in% c(2010,2011,2012,2013,2014,2015,2016,2017))
colnames(freedom_discussion)[1:3]<- c("code","year","freedom_discussion")
```

```{r}
index_discussion<- function (actual_value){
  ind<- (actual_value - 0)/(1-0)
  return(ind)
}
```
```{r}
freedom_discussion$freedom_discussion<-index_discussion(freedom_discussion$freedom_discussion)
```

####-----Freedom of domestic movement-----####

```{r}
freedom_domestic_movement<- select(freedom_of_domestic_movement, 2:4)
freedom_domestic_movement<- filter(freedom_domestic_movement, year %in% c(2010,2011,2012,2013,2014,2015,2016,2017))
colnames(freedom_domestic_movement)[1:3]<- c("code","year","freedom_domestic_movement")
```

```{r}
index_movement<- function (actual_value){
  ind<- (actual_value - 0)/(1-0)
  return(ind)
}
```
```{r}
freedom_domestic_movement$freedom_domestic_movement<-index_movement(freedom_domestic_movement$freedom_domestic_movement)
```


####----Life Satisfaction-----###


```{r}
life_satisfaction <- select(life_satisfaction, c(2:4))
life_satisfaction<- filter(life_satisfaction, Year %in% c(2010,2011,2012,2013,2014,2015,2016,2017))
colnames(life_satisfaction)[1:3]<- c("code","year","life_satisfaction")
```

```{r}
index_satisfaction<- function (actual_value){
  ind<- (actual_value - 0)/(10-0)
  return(ind)
}
```

```{r}
life_satisfaction$life_satisfaction <- index_satisfaction(life_satisfaction$life_satisfaction)
```

####------Economic Freedom Score-----###

```{r}
economic_freedom <- select(economic_freedom_score, c(2,1,4))
economic_freedom <- filter(economic_freedom, year %in% c(2010,2011,2012,2013,2014,2015,2016,2017))
colnames(economic_freedom)[1:3]<- c("code","year","economic_freedom")
```

```{r}
index_economic<- function (actual_value){
  ind<- (actual_value - 0)/(10-0)
  return(ind)
}
```

```{r}
economic_freedom$economic_freedom<- index_economic(economic_freedom$economic_freedom)
```


####-----Press Freedom----#####


```{r}
country_code <- select(vulnerability_employments,1:2)
colnames(country_code)[1:2] <- c("country","code")
press_freedom_score <- inner_join(country_code,press_freedom_score, by="country")

world_press_freedom_index <- press_freedom_score[c(-1,-3)]

colnames(world_press_freedom_index)[2:9]<- c("2010","2011","2012","2013","2014","2015","2016","2017")

```

```{r}
world_press_freedom_index$`2010`<- as.numeric(world_press_freedom_index$`2010`)
world_press_freedom_index$`2011`<- as.numeric(world_press_freedom_index$`2011`)
world_press_freedom_index$`2012`<- as.numeric(world_press_freedom_index$`2012`)
world_press_freedom_index$`2013`<- as.numeric(world_press_freedom_index$`2013`)
world_press_freedom_index$`2014`<- as.numeric(world_press_freedom_index$`2014`)
world_press_freedom_index$`2015`<- as.numeric(world_press_freedom_index$`2015`)
world_press_freedom_index$`2016`<- as.numeric(world_press_freedom_index$`2016`)
world_press_freedom_index$`2017`<- as.numeric(world_press_freedom_index$`2017`)
```

```{r}
index_press<- function (actual_value){
  ind<- (actual_value - 100)/(0-100)
  return(ind)
}
```

```{r}
world_press_freedom_index[2:9]<-index_press(world_press_freedom_index[2:9])
world_press_freedom_index <- gather(world_press_freedom_index,"year","press_freedom",2:9)
world_press_freedom_index$year<- as.integer(world_press_freedom_index$year)
```

##### Joining all the above tables created for the personal freedom and choice index ###


```{r}
personal_freedom <- left_join(vulnerability_employments_index,world_press_freedom_index, by=c("code","year")) 

personal_freedom <- left_join(personal_freedom,freedom_forced_labor, by=c("code","year"))

personal_freedom <- left_join(personal_freedom, freedom_discussion, by=c("code","year")) 

personal_freedom <- left_join(personal_freedom, freedom_domestic_movement, by=c("code","year"))

personal_freedom <- left_join(personal_freedom, life_satisfaction, by=c("code","year"))

personal_freedom <- left_join(personal_freedom, economic_freedom, by=c("code","year"))

```


```{r}

personal_freedom<-mutate(personal_freedom,personal_freedom_index= rowMeans(personal_freedom[,3:9],na.rm=T))
personal_freedom[,3:10]<-signif(personal_freedom[,3:10],digits=3)

```

### Personal safety index starts here ####


####----homocide------#####

```{r}
homicide <- select(homicide_country_data,c(1,6:13))
```

```{r}
colnames(homicide)[1:9]<- c("country","2010","2011","2012","2013","2014","2015","2016","2017")

homicide <- left_join(country_code,homicide, by="country")
homicide <- homicide[-1]
```

```{r}
index_homicide<- function (actual_value){
  ind<- (actual_value - 105.45)/(0-105.45)
  return(ind)
}
```

```{r}
homicide[2:9]<-index_homicide(homicide[2:9])
homicide<- gather(homicide,"year","homicide", 2:9)
homicide$year<- as.integer(homicide$year)
```


###----political killings-----###


```{r}
political_killings <- filter(political.killings, year %in% c(2010,2011,2012,2013,2014,2015,2016,2017))
political_killings <- political_killings[-1]
colnames(political_killings)[1] <- "code"

```

```{r}
index_political<- function (actual_value){
  ind<- (actual_value - 0)/(1-0)
  return(ind)
}
```

```{r}
political_killings$political_killings<-index_political(political_killings$political_killings)
political_killings$year <- as.integer(political_killings$year) 
```


###------deaths due to conflict and terrorism-----###


```{r}
conflict_terrorism_index<- select(deaths_conflict_terrorism_per_100000, c(2:4))
```

```{r}
colnames(conflict_terrorism_index)[1:3] <- c("code","year","conflict_terrorism_death")
conflict_terrorism_index<- filter(conflict_terrorism_index,year %in% c(2010,2011,2012,2013,2014,2015,2016,2017))
```

```{r}
index_conflict_terrorism<- function (actual_value){
  ind<- (actual_value - 100)/(0-100)
  return(ind)
}
```

```{r}
conflict_terrorism_index$conflict_terrorism_death<-index_conflict_terrorism(conflict_terrorism_index$conflict_terrorism_death)
```


#####----human rights protection index------#####


```{r}
human_rights_protection_index <- select(human_rights_scores,c(2:4))
colnames(human_rights_protection_index)[1:3] <- c("code","year","human_rights_protection")
```

```{r}
human_rights_protection_index<- filter(human_rights_protection_index, year %in% c(2010,2011,2012,2013,2014,2015,2016,2017))
```

```{r}
index_human_rights<- function (actual_value){
  ind<- (actual_value - (-3.8))/(5.4-(-3.8))
  return(ind)
}
```

```{r}
human_rights_protection_index$human_rights_protection<-index_human_rights(human_rights_protection_index$human_rights_protection)
```

####----rule of law----####

```{r}
rule_of_law_index <- select(rule_of_law,c(4,6:13))
```

```{r}
colnames(rule_of_law_index)[1:9] <-  c("code",2010,2011,2012,2013,2014,2015,2016,2017)
```

```{r}
index_rule_law<- function (actual_value){
  ind<- (actual_value - (-2.5))/(2.5-(-2.5))
  return(ind)
}
```

```{r}
rule_of_law_index$`2010`<- as.numeric(rule_of_law_index$`2010`)
rule_of_law_index$`2011`<- as.numeric(rule_of_law_index$`2011`)
rule_of_law_index$`2012`<- as.numeric(rule_of_law_index$`2012`)
rule_of_law_index$`2013`<- as.numeric(rule_of_law_index$`2013`)
rule_of_law_index$`2014`<- as.numeric(rule_of_law_index$`2014`)
rule_of_law_index$`2015`<- as.numeric(rule_of_law_index$`2015`)
rule_of_law_index$`2016`<- as.numeric(rule_of_law_index$`2016`)
rule_of_law_index$`2017`<- as.numeric(rule_of_law_index$`2017`)
```

```{r}
rule_of_law_index[2:9]<-index_rule_law(rule_of_law_index[2:9])

rule_of_law_index <- gather(rule_of_law_index,"year","rule_of_law", "2010":"2017")
rule_of_law_index$year <- as.integer(rule_of_law_index$year)
```



####---joining the tables for making the Personal safety index table---####



```{r}
personal_safety <- left_join(homicide,conflict_terrorism_index, by=c("code","year"))
personal_safety <- left_join(personal_safety,rule_of_law_index,by=c("code","year"))
personal_safety <- left_join(personal_safety,human_rights_protection_index,by=c("code","year"))
personal_safety <- left_join(personal_safety,political_killings,by=c("code","year"))
```

```{r}
personal_safety<-mutate(personal_safety,personal_safety_index= rowMeans(personal_safety[,3:7],na.rm=T))
personal_safety[,3:8]<-signif(personal_safety[,3:8],digits=3)
```


##### Combining personal_safety_index and personal freedom index table ####



```{r}
s_index <- left_join(personal_freedom,personal_safety, by = c("code","year"))
s_index <- select(s_index, c(1:9,c(11:16,10)))
s_index<- left_join(country_code, s_index, by="code") 
skim(s_index)
```



#### Below codes are to calulate personal rights index and inclusiveness index  ####



```{r}
PR<- File.for.Political.rights
DIS<-File.for.Discrimination.against.minorities.
VDEM<-File.for.V.Dem
CE<- File.for.clean.environment.
IA<- File.for.Internet.access
```

```{r}
country_code<- country_code[-1]
colnames(country_code)[1:2] <- c("Country","Code")
country_continent <- left_join(country_code, Continents., by= "Code")
country_continent <- country_continent[-3]
colnames(country_continent)[1] <- "Country" 
country_continent<- na.omit(country_continent)
```

```{r}
colnames(PR)[3]<- "Political Rights"
PR<- subset(PR, Year %in% c("2010", "2011", "2012", "2013", "2014","2015", "2016", "2017"))
PR$Year<- as.numeric(PR$Year)
PR<- arrange(PR, Year)
PR<- arrange(PR, Country)
PR<- left_join(PR, country_continent, by="Country")
PR<- PR[,c(1,4,5,2,3)]
```

```{r}
DIS<- separate(DIS, Year, sep="-", into = c("Year", "Month", "Day"), remove= TRUE)
DIS$Month<- NULL
DIS$Day<-NULL
colnames(DIS)[3]<- "Discrimination against minorities"
DIS<- subset(DIS,  Year %in% c("2010", "2011", "2012", "2013", "2014","2015", "2016", "2017"))
DIS$Year<- as.numeric(DIS$Year)
DIS<- arrange(DIS, Year)
DIS<- arrange(DIS, Country)
DIS<- left_join( DIS,country_continent, by="Country")
DIS<- DIS[,c(1,4,5,2,3)]
```

```{r}
VDEM$country_id<- NULL
colnames(VDEM)<- c("Country","Year","Freedom of Expression", "Freedom of Religion", "Property Rights for Women", "Access to Justice", "Political Power by Socioeconomic Class", "Political Power by Social Group", "Political Power by Gender" )
VDEM<-subset(VDEM, Year %in% c("2010", "2011", "2012", "2013", "2014","2015", "2016", "2017"))
VDEM$Year<- as.numeric(VDEM$Year)
VDEM<- left_join(VDEM,country_continent, by="Country")
VDEM<- VDEM[,c(1,10,11,2,3,4,5,6,7,8,9)]
```

```{r}
colnames(CE)<- c("Country", "Clean Environment", "Year")
CE<- subset(CE,Year %in% c("2010", "2011", "2012", "2013", "2014","2015", "2016", "2017"))
CE$`Clean Environment`<- as.numeric(CE$`Clean Environment`)
CE[,2] <- signif(CE[,2], digits=5)
CE<- arrange(CE, Year)
CE<- arrange(CE, Country)
CE<- left_join(CE,country_continent, by="Country")
CE<- CE[,c(1,4,5,3,2)]
```

```{r}
IA<-gather(IA,Year,InternetAccess,2:12)
colnames(IA)<- c("Country", "Year", "Access to internet")
IA<- subset(IA,Year %in% c("2010", "2011", "2012", "2013", "2014","2015", "2016", "2017"))
IA$Year<- as.numeric(IA$Year)
IA<- arrange(IA, Year)
IA<- arrange(IA, Country)
IA<- left_join(IA,country_continent, by="Country")
IA<- IA[,c(1,4,5,2,3)]
```

```{r}
PRDIS<- left_join(PR, DIS, by=c("Year", "Region", "Code", "Country"))

PRDISVDEM<-left_join(PRDIS, VDEM, by=c("Year", "Region", "Code", "Country"))

PRDISVDEMCE<- left_join(PRDISVDEM,CE, by=c("Year", "Region", "Code","Country"))

PRDISVDEMCEIA<- left_join(PRDISVDEMCE,IA, by=c("Year", "Region", "Code", "Country"))
```

```{r}

Final_table<-PRDISVDEMCEIA
Final_table<-Final_table[, c(1,2,3,4,5,7,8,10,9,15,14,6,13,11,12)]
```

```{r}
Indexed_Table<- Final_table

Indexed_Table$`political rights`<- Final_table$`Political Rights`/40
Indexed_Table$`discrimination_against_minorities`<- (Final_table$`Discrimination against minorities`-1)/9
Indexed_Table$`freedom_of_expression`<- Final_table$`Freedom of Expression`
Indexed_Table$`freedom_of_religion`<- Final_table$`Freedom of Religion`/4
Indexed_Table$`property_rights_for_women`<- Final_table$`Property Rights for Women`/5
Indexed_Table$`access_to_justice`<- Final_table$`Access to Justice`/1
Indexed_Table$`political_power_by_socioeconomic_class`<- Final_table$`Political Power by Socioeconomic Class`/4
Indexed_Table$`political_power_by_social_group`<- Final_table$`Political Power by Social Group`/4
Indexed_Table$`political_power_by_gender`<- Final_table$`Political Power by Gender`/4
Indexed_Table$`access_to_internet`<- Final_table$`Access to internet`/100
Indexed_Table$`clean_environment`<- Final_table$`Clean Environment`/100

```

```{r}
colnames(Indexed_Table)[c(1:4)]<-c("country", "code","region","year")
Indexed_Table[,c(5:15)]<-NULL
Indexed_Table[is.na(Indexed_Table)]<-0
```

```{r}
Indexed_Table$personal_rights_index<- (Indexed_Table$`political rights`+ Indexed_Table$freedom_of_expression + Indexed_Table$freedom_of_religion + Indexed_Table$access_to_justice + Indexed_Table$property_rights_for_women + Indexed_Table$access_to_internet + Indexed_Table$clean_environment)/7
Indexed_Table$inclusiveness_index<- (Indexed_Table$discrimination_against_minorities + Indexed_Table$political_power_by_gender + Indexed_Table$political_power_by_socioeconomic_class + Indexed_Table$political_power_by_social_group)/4

k_code <- Indexed_Table
```


####----Creating a final table for visualization----####



```{r}
final_table <- left_join(k_code,s_index, by=c("code","year"))
final_table <- final_table[-18]
colnames(final_table)[1] <- "country"

final_table <- select(final_table,c(1:15,c(18:31,16:17)))
final_table <- mutate(final_table,liberty_index= rowMeans(final_table[,28:31],na.rm=T))
```



#####------combining gdp/capita and life exp data with final_table-----#####


```{r}
gdp_life_exp_1 <- gdp_life_exp[-c(1:2)]

final_table<- left_join(final_table,gdp_life_exp_1,by=c("code","year")) 
final_table$life_exp_at_birth <- as.numeric(final_table$life_exp_at_birth)
final_table <- filter(final_table, region != 0 | !is.na(income_group))
```



```{r}
happiness_index<-WHR2018Chapter2OnlineData
happiness_index<- filter(happiness_index, year %in% c(2010,2011,2012,2013,2014,2015,2016,2017))
happiness_index<- select(happiness_index, 1:3)
#happiness_plot<- left_join(happiness_index,table_for_plots, by=c("country","year"))
colnames(happiness_index)[c(1,3)]<- c("Country","happiness_score") 
#happiness_plot <- filter(happiness_plot, region !=0 | income_group != "NA")
happiness_index$happiness_index<- (happiness_index$happiness_score-2.66)/5.35
happiness_index <- happiness_index[-3]
```

```{r}
happiness_index <- left_join(happiness_index,Continents.,by="Country")
happiness_index <- happiness_index[-1]
colnames(happiness_index) <- tolower(colnames(happiness_index))
```

```{r}
final_table <- left_join(final_table,happiness_index,by=c("code","region","year"))

```

```{r}
write.csv(final_table,"final_table_project.csv", row.names = F)
```

##### Final Code for Vizualization with final table #####

```{r}

final_table_project$vulnerability_employment <- str_replace_all(final_table_project$vulnerability_employment,"NA","0")
final_table_project$press_freedom <- str_replace_all(final_table_project$press_freedom,"NA","0")
final_table_project$freedom_forced_labor <- str_replace_all(final_table_project$freedom_forced_labor,"NA","0")
final_table_project$freedom_discussion <- str_replace_all(final_table_project$freedom_discussion,"NA","0")
final_table_project$freedom_domestic_movement <- str_replace_all(final_table_project$freedom_domestic_movement,"NA","0")
final_table_project$life_satisfaction <- str_replace_all(final_table_project$life_satisfaction,"NA","0")
final_table_project$economic_freedom <- str_replace_all(final_table_project$economic_freedom,"NA","0")
final_table_project$personal_freedom_index <- str_replace_all(final_table_project$personal_freedom_index,"NA","0")
final_table_project$homicide <- str_replace_all(final_table_project$homicide,"NA","0")
final_table_project$conflict_terrorism_death <- str_replace_all(final_table_project$conflict_terrorism_death,"NA","0")
final_table_project$rule_of_law <- str_replace_all(final_table_project$rule_of_law,"NA","0")
final_table_project$human_rights_protection <- str_replace_all(final_table_project$human_rights_protection,"NA","0")
final_table_project$political_killings <- str_replace_all(final_table_project$political_killings,"NA","0")
final_table_project$personal_safety_index <- str_replace_all(final_table_project$personal_safety_index,"NA","0")
final_table_project$happiness_index <- str_replace_all(final_table_project$happiness_index,"NA","0")
final_table_project$GDP <- str_replace_all(final_table_project$GDP,"NA","0")
final_table_project$life_exp_at_birth <- str_replace_all(final_table_project$life_exp_at_birth,"NA","0")
final_table_project$vulnerability_employment <- as.numeric(final_table_project$vulnerability_employment)
final_table_project$press_freedom <- as.numeric(final_table_project$press_freedom)
final_table_project$freedom_forced_labor <- as.numeric(final_table_project$freedom_forced_labor)
final_table_project$freedom_discussion <- as.numeric(final_table_project$freedom_discussion)
final_table_project$freedom_domestic_movement <- as.numeric(final_table_project$freedom_domestic_movement)
final_table_project$life_satisfaction <- as.numeric(final_table_project$life_satisfaction)
final_table_project$economic_freedom <- as.numeric(final_table_project$economic_freedom)
final_table_project$personal_freedom_index <- as.numeric(final_table_project$personal_freedom_index)
final_table_project$homicide <- as.numeric(final_table_project$homicide)
final_table_project$conflict_terrorism_death <- as.numeric(final_table_project$conflict_terrorism_death)
final_table_project$rule_of_law <- as.numeric(final_table_project$rule_of_law)
final_table_project$human_rights_protection <- as.numeric(final_table_project$human_rights_protection)
final_table_project$political_killings <- as.numeric(final_table_project$political_killings)
final_table_project$personal_safety_index <- as.numeric(final_table_project$personal_safety_index)
final_table_project$happiness_index <- as.numeric(final_table_project$happiness_index)
final_table_project$GDP <- as.numeric(final_table_project$GDP)
final_table_project$life_exp_at_birth <- as.numeric(final_table_project$life_exp_at_birth)
```

```{r}
final_table_project <- filter(final_table_project, region != 0 | !is.na(income_group))
```


####--- creating viz-----####


```{r}
viz_table <- select(final_table_project,c(1,3:4,28:32))
viz_table[,4:8]<- signif(viz_table[,4:8], digits=3)
```

```{r}
viz_line <- select(viz_table,c(2:3,8))
viz_line <- summarise(group_by(viz_line,region,year), liberty_index = median(liberty_index))
world_rows <- summarise(group_by(viz_line,year),liberty_index= median(liberty_index))
world_rows$region <- "World"
world_rows<- select(world_rows, c(3,1:2))
viz_line<-bind_rows(viz_line,world_rows)
viz_line <- filter(viz_line, region != 0)
viz_line$liberty_index <- signif(viz_line$liberty_index, digits=2)


ggplot(viz_line, aes(x=year,y=liberty_index,col=region)) + geom_line(size=2)+ geom_point(size=2,color="black")+ scale_x_continuous(breaks = c(2010,2011,2012,2013,2014,2015,2016,2017))+labs(x="Year",y="Liberty Index",title = "Liberty Index of Continents (2010-2017)")+theme(panel.grid.minor= element_blank(),panel.grid.major.x = element_blank(),panel.background = element_rect(fill="grey90"),plot.title = element_text(face="bold",hjust = 0.5,size=15),panel.border = element_rect(colour = "black", fill=NA, size=1.5),axis.text = element_text(face="bold",size = 8),axis.title = element_text(face="bold",size = 12))+theme(legend.position = c(.45,.8),legend.title = element_blank(),legend.direction = "horizontal",legend.key.height = unit(.75,"line"),legend.key.width = unit(3,"line"))+scale_color_brewer(palette = "Dark2")
```



```{r}
viz_rad <- select(viz_table,2:8)
viz_rad <- summarise_each(group_by(viz_rad,region,year),funs(median),personal_safety_index:liberty_index)
colnames(viz_rad)[3:7]<- c("Personal Safety","Personal Rights","Inclusiveness","Personal Freedom","Liberty Index")
```

```{r}
viz_rad_2010 <- filter(viz_rad, year==2010)
viz_rad_2010<-viz_rad_2010[-c(2,7)]
viz_rad_2010 <- gather(viz_rad_2010,"index","value",2:5)
viz_rad_2010 <- spread(viz_rad_2010,region,value)
c <- grDevices::col2rgb(c("orange","purple4", "hotpink","red","black","green"))
chartJSRadar(scores = viz_rad_2010,maxScale = 1,fontsize=18,width = 350, height=220,scaleStepWidth = .1,labelSize = 15,addDots = T,polyAlpha = .08,lineAlpha = 50,colMatrix =c,main = "2010")
```

```{r}

viz_rad_2016 <- filter(viz_rad, year==2016)
viz_rad_2016<-viz_rad_2016[-c(2,7)]
viz_rad_2016 <- gather(viz_rad_2016,"index","value",2:5)
viz_rad_2016 <- spread(viz_rad_2016,region,value)
chartJSRadar(scores = viz_rad_2016,maxScale = 1,fontsize=18,width = 350, height=220,scaleStepWidth = .1,labelSize = 15,addDots = T,polyAlpha = .08,lineAlpha = 50,colMatrix =c,main = "2016")
```

```{r}
viz_rad_2017 <- filter(viz_rad, year==2017)
viz_rad_2017<-viz_rad_2017[-c(2,7)]
viz_rad_2017 <- gather(viz_rad_2017,"index","value",2:5)
viz_rad_2017 <- spread(viz_rad_2017,region,value)
chartJSRadar(scores = viz_rad_2017,maxScale = 1,fontsize=18,width = 350, height=220,scaleStepWidth = .1,labelSize = 15,addDots = T,polyAlpha = .08,lineAlpha = 50,colMatrix =c,main = "2017")
```

```{r}
table_for_plots<- final_table_project
table_for_plots <- filter(table_for_plots, region !=0 | income_group != "NA")
```

```{r}
p2<-ggplot(data=table_for_plots, mapping= aes(x=GDP, y=liberty_index,color=region, shape=income_group)) + geom_point(size=2.5,alpha=.8) + scale_x_log10()+ scale_y_continuous(breaks= seq(0.2,1,0.1), limits = c(0.2,0.9))
p3<- p2 + geom_hline(yintercept = c(0.4,0.7))+ geom_vline(xintercept = c(1000,5000,10000))+ labs(x="log GDP",y="Liberty Index",title = "Liberty Index vs GDP (2010-2017)")+theme(panel.background = element_rect(fill="grey90"),plot.title = element_text(face="bold",hjust = 0.5,size=15),panel.border = element_rect(colour = "black", fill=NA, size=1.5),axis.text = element_text(face="bold",size = 8),axis.title = element_text(face="bold",size = 12))+labs(color="Region", shape="Income Group")
p3
```

```{r}
happiness_plot <- select(final_table_project,region, income_group, happiness_index,liberty_index)
happiness_plot <- filter(happiness_plot,happiness_index != 0)

p4<- ggplot(data=happiness_plot, mapping= aes(x=happiness_index, y=liberty_index,color=region, shape=income_group)) + geom_point(size=2.5,alpha =.8)+ scale_x_continuous(breaks= seq(0,1,0.1)) + scale_y_continuous(breaks= seq(0.2,1,0.1), limits=c(0.2,0.9))
p5<- p4+ geom_vline(xintercept = c(0.3,0.6)) + geom_hline(yintercept = c(0.4,0.7))+labs(x="Happiness Index",y="Liberty Index",title = "Liberty Index vs Happiness Index (2010-2017)")+theme( panel.background = element_rect(fill="grey90"),plot.title = element_text(face="bold",hjust = 0.5,size=15),panel.border = element_rect(colour = "black", fill=NA, size=1.5),axis.text = element_text(face="bold",size = 8),axis.title = element_text(face="bold",size = 12))+labs(color="Region", shape="Income Group")
p5  
```







